Supplementary Material to ``External Prior Guided Internal Prior Learning for Real Noisy Image Denoising"

### 2016-11-15 1047_sp.tex
a

>>>>

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 34.90dB }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 34.92dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 34.99dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
{\footnotesize (d) MLP \cite{mlp}: 37.01dB }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
{\footnotesize (e) CSF \cite{csf}: 37.94dB }
\end{minipage}
}\vspace{-3mm}
\subfigure{
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 38.13dB   }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
{\footnotesize (g) NI \cite{neatimage}: 37.24dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 38.11dB   }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
{\footnotesize (i) Ours: \textbf{38.95}dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}
\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A2" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\label{fig17}
\end{figure}
